Topic Scores

### 2019-02-19 Topic Scores.Rmd
figuring out course to keyword mapping

##getting top courses per student
```{r topic score student}
student$topic_score <- beta_description$k35%>%
  filter(term %in% student$kw_policy) %>%
  group_by(topic)%>% #maybe we can do this with transcripts afterwards
  summarize(B_score= sum(beta))%>%
  ungroup()%>%
  mutate(Total_b      = sum(B_score),
         B_proportion = B_score/Total_b) %>%
  arrange(desc(B_score))

>>>>

##getting top courses per student
```{r topic score student}
student$topic_score <- beta_description$k35 %>%
  filter(term %in% student$kw_policy)       %>%
  group_by(topic)                           %>% #maybe we can do this with transcripts afterwards
  summarize(B_score= sum(beta))             %>%
  ungroup()                                 %>%
  mutate(Total_b      = sum(B_score),
         B_proportion = B_score/Total_b)    %>%
  arrange(desc(B_score))

### 2019-02-19 test_delete_later_sofia.Rmd
figuring out course to keyword mapping

##Topic contribution to course
```{r course_score}

#
## Topic contribution to course
gamma_descriptions$k35     %>%
  full_join(student$topic_score, by = "topic") %>%
  group_by(document, topic)                           %>%
  summarise(total_gamma= sum(gamma))
  mutate(X = gamma * B_proportion)             %>%
  group_by(document)                           %>%
  summarise(course_score = sum(X))             %>%
  arrange(desc(course_score))                  %>%
  left_join(
    select(d_course, `Course ID`, `Course Title`),
    by = c("document" = "Course ID")
    )

>>>>

##Topic contribution to course
```{r course_score}
my_courses <- top_n(x = student$course_score, n = 5, wt =course_score) %>% 
  pull(document)

#
## Topic contribution to course
gamma_descriptions$k35     %>%
  filter(document %in% my_courses)%>%
  arrange(document, gamma)
  full_join(student$topic_score, by = "topic") %>%
  group_by(document, topic)                           %>%
  summarise(total_gamma= sum(gamma))
  mutate(X = gamma * B_proportion)             %>%
  group_by(document)                           %>%
  summarise(course_score = sum(X))             %>%
  arrange(desc(course_score))                  %>%
  left_join(
    select(d_course, `Course ID`, `Course Title`),
    by = c("document" = "Course ID")
    )
